---
title: "About"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
#options(knitr.table.format = "latex")
options(knitr.table.format = "html")
```

## Seoncheol Park

````{=html}
<!--
```{r}
getRandomNumber <- function() {
  sample(1:6, 1)
}
```

```{asis, echo = getRandomNumber() == 4}
According to https://xkcd.com/221/, we just generated
a **true** random number!
```
-->
````

Now I am an assistant professor at the [Department of Mathematics](http://math.hanyang.ac.kr/) and the [Department of Applied Statistics](http://stat.hanyang.ac.kr/) at [Hanyang University](https://www.hanyang.ac.kr/), South Korea. Before joining Hanyang University, I worked as an assistant professor at the [Department of Information Statistics](http://stat.chungbuk.ac.kr), [Chungbuk National University](http://www.cbnu.ac.kr) for two years. Also, I was a post-doctoral research fellow at the [Pacific Climate Impacts Consortium](https://www.pacificclimate.org/) under the supervision of Prof. [Francis Zwiers](https://www.pacificclimate.org/about-pcic/people/francis-zwiers). I received my Ph.D. degree in statistics at Seoul National University under the supervision of Prof. [Hee-Seok Oh](https://sites.google.com/site/heeseokoh). I was also a member of [Multiscale Methods in Statistics Lab](https://sites.google.com/view/snumultiscale/home).

## Professional Experiences

-   Assistant Professor, [Department of Mathematics](http://math.hanyang.ac.kr/) and [Department of Applied Statistics](http://stat.hanyang.ac.kr/), [Hanyang University](https://www.hanyang.ac.kr/), Seoul, Korea, March 2023 \~

-   Assistant Professor, [Department of Information Statistics](http://stat.chungbuk.ac.kr), [Chungbuk National University](http://www.cbnu.ac.kr), Cheongju, Korea, March 2021 \~ February 2023.

-   Post-Doctoral Research Fellow, [Pacific Climate Impacts Consortium](https://www.pacificclimate.org/), [University of Victoria](https://www.uvic.ca), Victoria, British Columbia, Canada, August 2019 \~ January 2021.

## Education

-   Ph.D., Statistics, [Seoul National University](http://www.snu.ac.kr), Seoul, Korea, 2019.

-   B.S., Mathematical Sciences (Double Major with Management Sciences), [KAIST](http://www.kaist.ac.kr), Daejeon, Korea, 2013.

## Research Interests

-   Spatio-temporal data analysis and extreme value statistics, application to environmental and public health data

## Academic Works

::: panel-tabset
## Publications

### International Journal Papers

(${}^\ast$: Corresponding author, and ${}^{\ast\ast}$: Students I supervised)

::: {}

1. S. Kang, K. Kim, Y. Kwon, S. Park, **S. Park**, H-Y. Shin, J. Kim${}^\ast$ and H-S. Oh (2024+). [Semiparametric approaches for the inference of univariate and multivariate extremes.](https://link.springer.com/article/10.1007/s10687-024-00497-x) *Extremes*, In press.

1. B. Lee, H-D. Sou${}^\ast$, P. Yeon, H. Lee, C-R. Park, S. Choi and **S. Park**${}^\ast$ (2024). [Seasonal Characteristics of Particulate Matter by Pollution Source Type and Urban Forest Type.](https://doi.org/10.3390/app14219988) *Applied Sciences*, **14(21)**, 9988.

1. S. Cho, D-K. Kim, M-C. Song, E. Lee, **S. Park**, D. Chung and J. Ha${}^\ast$ (2024). [Deciphering changes in the incidence of hemorrhagic stroke and cerebral venous sinus thrombosis during the coronavirus disease 2019 pandemic: a nationwide time-series correlation study.](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0301313) *PLOS ONE*, **19(10)**, e0301313.

1.  H. Lee, D. Kwon, **S. Park**, S-R. Park, , D. Chung and J. Ha${}^\ast$ (2023). [Temporal association between age-specific incidence of Guillain--Barré syndrome and SARS-CoV-2 vaccination; a nationwide time-series correlation study.](https://doi.org/10.24171/j.phrp.2023.0050) *Osong Public Health and Research Perspectives*, **14(3)**, 224--231.

1.  J. Lee${}^{\ast\ast}$ and **S. Park**${}^\ast$ (2023). [Prediction of sharp change of particulate matter in Seoul via quantile mapping.](https://doi.org/10.29220/CSAM.2023.30.3.259) *Communications for Statistical Applications and Methods*, **30(3)**, 259--272.

1.  B. Lee${}^{\ast\ast}$, P. Yeon and **S. Park**${}^\ast$ (2022). [The factors and relationships influencing urban hiking exercise characteristics after COVID-19 occurrence: at Seoul Metropolitan Area and in their 20s and 30s.](https://www.mdpi.com/1660-4601/19/24/16403) *International Journal of Environmental Research and Public Health*, **19(24)**, 16403.

1.  S. Cho, Y-M. Kim, G. Seong, S. Park, **S. Park**, S-E. Lee and Y. Park${}^\ast$ (2022). [Analysis of on-ship transmission through cases of COVID-19 mass outbreak on Republic of Korea Navy Amphibious Warfare ship.](https://doi.org/10.4178/epih.e2022065) *Epidemiology and Health*, **44**, e2022065.

1.  S. Lee, **S. Park** and Y. Lim${}^\ast$ (2022). [Prediction of extreme PM2.5 concentrations via extreme quantile regression.](https://doi.org/10.29220/CSAM.2022.29.3.319) *Communications for Statistical Applications and Methods*, **29(3)**, 319--331.

1.  **S. Park** and H-S. Oh${}^\ast$ (2022). [Lifting scheme for streamflow data in river networks.](https://rss.onlinelibrary.wiley.com/doi/10.1111/rssc.12542) *Journal of the Royal Statistical Society: Series C (Applied Statistics)*, **71(2)**, 467--490.

1.  J. Kim, **S. Park**${}^\ast$, J. Kwon, Y. Lim and H-S. Oh (2021). [Estimation of spatio-temporal extreme distribution using a quantile factor model.](https://link.springer.com/article/10.1007/s10687-020-00404-0) *Extremes*, **24(1)**, 177--195.

1.  **S. Park**${}^\ast$, J. Kwon, J. Kim and H-S. Oh (2018). [Prediction of extremal precipitation by quantile regression forests: from SNU Multiscale team.](https://link.springer.com/article/10.1007/s10687-018-0323-y) *Extremes*, **21(3)**, 463--476.

1.  **S. Park** and H-S. Oh${}^\ast$ (2017). [Spatio-temporal analysis of particulate matter extremes in Seoul: use of multiscale approach.](http://dx.doi.org/10.1007/s00477-016-1376-6) *Stochastic Environmental Research and Risk Assessment*, **31(9)**, 2401--2414.

:::

```{=html}
<!--
1. **S. Park** and H-S. Oh${}^\ast$ (2022). [Lifting scheme for streamflow data in river networks.](https://rss.onlinelibrary.wiley.com/doi/10.1111/rssc.12542) *Journal of the Royal Statistical Society: Series C (Applied Statistics)*, **71(2)**, 467--490. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. J. Kim, **S. Park**${}^\ast$, J. Kwon, Y. Lim and H-S. Oh (2021). [Estimation of spatio-temporal extreme distribution using a quantile factor model.](https://link.springer.com/article/10.1007/s10687-020-00404-0) *Extremes*, **24(1)**, 177--195. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. **S. Park**${}^\ast$, J. Kwon, J. Kim and H-S. Oh (2018). [Prediction of extremal precipitation by quantile regression forests: from SNU Multiscale team.](https://link.springer.com/article/10.1007/s10687-018-0323-y) *Extremes*, **21(3)**, 463--476. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. **S. Park** and H-S. Oh${}^\ast$ (2017). [Spatio-temporal analysis of particulate matter extremes in Seoul: use of multiscale approach.](http://dx.doi.org/10.1007/s00477-016-1376-6) *Stochastic Environmental Research and Risk Assessment*, **31(9)**, 2401--2414. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`
-->
```
```{=html}
<!--
### Under Review
-->
```
```{=html}
<!--
1. S. Lee, **S. Park** and Y. Lim${}^\ast$ (2021+). Prediction of extreme PM2.5 concentrations via extreme quantile regression. *Communications for Statistical Applications and Methods*, Accepted for publication.
-->
```
```{=html}
<!--
1. S. Cho, Y-M. Kim, G. Seong, S. Park, **S. Park**, S-E. Lee and Y. Park${}^\ast$ (2022+). Analysis of on-ship transmission through cases of COVID-19 mass outbreak on Republic of Korea Navy Amphibious Warfare ship. *Epidemiology and Health]*.
-->
```
## Presentations

::: {}

1. [Clustering of Mountain Hiking GPS-Trajectory Data](https://webpageprodvm.ntu.edu.tw/IASC-ARS_Interim_2024/cp.aspx?n=190889), *IASC-ARS Interim Conference 2024*, Taipei, Taiwan, December 2024.

1. Estimation of marine heatwaves in the East Sea: The extreme value generalized additive model approach, *Asia Oceania Geosciences Society (AOGS) 2024 21^th^ Annual Meeting*, Pyeongchang, Korea, June 2024.

1.  Spatial statistical models for environmental data in Korea, *Japanese Joint Statistical Meeting 2022*, Tokyo, Japan, September 2022.

1. Prediction of sharp change of particulate Matter in Seoul via quantile mapping (with Jeongeun Lee), *2022 The Korean Statistical Society Spring Conference*, Seoul, Korea, June 2022.

1.  Lifting scheme for streamflow data in river networks, *2022 The Korean Data Information Science Society Spring Conference*, Busan, Korea, May 2022.

1.  Lifting scheme for streamflow data in river networks, *2021 The Korean Statistical Society Autumn Conference*, Seoul, Korea, November 2021.

1.  Lifting scheme for streamflow data in river networks, *Bernoulli-IMS 10^th^ World Congress in Probability and Statistics*, Seoul, Korea, July 2021.

1.  A new approach for modelling the spatial extent of agricultural drought, *The 55^th^ Canadian Meteorological and Oceanographic Society (CMOS) Congress*, Victoria, Canada, June 2021.

1.  Multiresolution analysis for spatio-temporal data, *5^th^ Institute of Mathematical Statistics Asia Pacific Rim Meeting*, Singapore, Singapore, June 2018.

1.  [Prediction of extremal precipitation: the use of quantile regression forests](http://www.eva2017.nl/program/scipro/friday/index.html), *10^th^ Extreme Value Analysis Conference*, Delft, Netherlands, June 2017.

1.  Multiresolution analysis for spatio-temporal data. *2017 The Korean Statistical Society Spring Conference*, Seoul, Korea, May 2017.

1.  Multiscale modeling for particulate matter extremes. *2015 The Korean Statistical Society Autumn Conference*, Yongin, Korea, November 2015.

1. [Multiscale modeling for particulate matter extremes in Seoul](http://data.si.re.kr/node/623). *The Seoul Institute Research Competition 2015*, Seoul, Korea, November 2015.

1. Prediction of extreme particulate matter : the use of quantile regression forests. *2014 The Korean Statistical Society Autumn Conference*, Seoul, Korea, November 2014.

:::

## Awards

::: {}

1.  Excellence award (3rd place), KSIAM-MathWorks problem challenge, *Korea Society for Industrial and Applied Mathematics*, Sep 2018.

1.  Best oral presentation award (Pre-PhD): Multiresolution analysis for spatio-temporal data. *The Korean Statistical Society*, May 2017.

1.  Excellence award, [The Seoul Institute Research Competition 2015](http://data.si.re.kr/node/623), *The Seoul Institute*, November 2015.

:::

## Grants

### International or Domestic Research Foundations

- Outstanding Young Scientist Grants (우수신진연구), *Korean Ministry of Science and ICT*, April 2024 \~ March 2027.

-   Basic Science Research Program (기본연구), *Korean Ministry of Education*, June 2021 \~ August 2024.

### University Grants

- 서울-ERICA 공동연구 지원사업, *Hanyang University (HYU)*, June 2024 \~ May 2025.

-   신임교원 정착 연구 지원사업, *Hanyang University (HYU)*, March 2023 \~ August 2024.

-   신진교수 연구비 지원사업, *Chungbuk National University (CBNU)*, March 2021 \~ August 2022.

### Scholarship

-   Sohn Dong-Joon Scholarship, *College of Natural Sciences (SNU)*, May 2016 \~ August 2019.

## Services

### Referee

-   Theoretical and Applied Climatology

-   Annals of Applied Statistics

-   Journal of Agricultural, Biological and Environmental Statistics

-   Extremes

-   Stochastic Environmental Research and Risk Assessment

-   Computational Statistics

-   Journal of the Korean Statistical Society

-   Communications for Statistical Applications and Methods

-   Computational Statistics and Data Analysis

-   Scientific Reports

### Professional Services

- 한국통계학회 평의원

- 서울특별시 스마트도시위원회 위원

## Teaching

### Hanyang University

#### Undergraduate Courses

-   Statistical Computing (2023 Fall, 2024 Fall)

-   Introduction to Regression Analysis (2024 Spring)

-   Artificial Intelligence and Machine Learning (2023 Spring, 2024 Spring, 2025 Spring)

#### Graduate Courses

-   Regression Analysis (2024 Spring)

-   Nonparametric Statistics (2024 Fall)

-   Linear Models (2025 Spring)

-   Statistical Data Science (2023 Fall)

-   Seminar in Recent Development of Applied Statistics (2023 Spring)

### Chungbuk National University

#### Undergraduate Courses

-   Elementary Probability Theory (2022 Spring)

-   Regression Analysis (2021 Spring, 2022 Spring)

-   Statistical Simulation (2021 Spring)

-   Insurance Statistics (2021 Fall)

-   Financial Statistics (2021 Fall)

-   Financial and Insurance Statistics (2022 Fall)

-   Spatial Statistics (2022 Fall)

#### Graduate Courses

-   Topics in Regression Analysis (2022 Spring)

-   Statistical Methodology (2021 Spring)

-   Machine Learning Methodology (2022 Fall)

-   Deep Learning (2021 Fall)
:::

## Contact Me

[pscstat\@hanyang.ac.kr](mailto:pscstat@hanyang.ac.kr) or [pscstat\@gmail.com](mailto:pscstat@gmail.com)
