---
title: "About"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
#options(knitr.table.format = "latex")
options(knitr.table.format = "html")
```

## Seoncheol Park

````{=html}
<!--
```{r}
getRandomNumber <- function() {
  sample(1:6, 1)
}
```

```{asis, echo = getRandomNumber() == 4}
According to https://xkcd.com/221/, we just generated
a **true** random number!
```
-->
````

Now I am an assistant professor at the [Department of Information Statistics](http://stat.chungbuk.ac.kr), [Chungbuk National University](http://www.cbnu.ac.kr), South Korea. Before joining Chungbuk National University, I was a post-doctoral research fellow at the [Pacific Climate Impacts Consortium](https://www.pacificclimate.org/), under the supervision of Prof. [Francis Zwiers](https://www.pacificclimate.org/about-pcic/people/francis-zwiers). I received my Ph.D. degree in statistics at Seoul National University, under the supervision of Prof. [Hee-Seok Oh](https://sites.google.com/site/heeseokoh). I was also a member of [Multiscale Methods in Statistics Lab](https://sites.google.com/view/snumultiscale/home).

## Professional Experiences

-   Assistant Professor, [Department of Information Statistics](http://stat.chungbuk.ac.kr), [Chungbuk National University](http://www.cbnu.ac.kr), Cheongju, Korea, March 2021 \~

-   Post-Doctoral Research Fellow, [Pacific Climate Impacts Consortium](https://www.pacificclimate.org/), [University of Victoria](https://www.uvic.ca), Victoria, British Columbia, Canada, August 2019 \~ January 2021.

## Education

-   Ph.D., Statistics, [Seoul National University](http://www.snu.ac.kr), Seoul, Korea, 2019.

-   B.S., Mathematical Sciences (Double Major with Management Sciences), [KAIST](http://www.kaist.ac.kr), Daejeon, Korea, 2013.

## Research Interests

-   Spatio-temporal data analysis and extreme value statistics, application to environmental data

## Academic Works

::: panel-tabset
## Publications

### International Journal Papers

(<sup>$*$</sup>: Corresponding author)


1. S. Cho, Y-M. Kim, G. Seong, S. Park, **S. Park**, S-E. Lee and Y. Park<sup>$*$</sup> (2022+). [Analysis of on-ship transmission through cases of COVID-19 mass outbreak on Republic of Korea Navy Amphibious Warfare ship.](https://doi.org/10.4178/epih.e2022065) *Epidemiology and Health*, Accepted for publication.

1.  S. Lee, **S. Park** and Y. Lim<sup>$*$</sup> (2022). [Prediction of extreme PM2.5 concentrations via extreme quantile regression.](https://doi.org/10.29220/CSAM.2022.29.3.319) *Communications for Statistical Applications and Methods*, **29(3)**, 319--331.

2.  **S. Park** and H-S. Oh<sup>$*$</sup> (2022). [Lifting scheme for streamflow data in river networks.](https://rss.onlinelibrary.wiley.com/doi/10.1111/rssc.12542) *Journal of the Royal Statistical Society: Series C (Applied Statistics)*, **71(2)**, 467--490.

3.  J. Kim, **S. Park**<sup>$*$</sup>, J. Kwon, Y. Lim and H-S. Oh (2021). [Estimation of spatio-temporal extreme distribution using a quantile factor model.](https://link.springer.com/article/10.1007/s10687-020-00404-0) *Extremes*, **24(1)**, 177--195.

4.  **S. Park**<sup>$*$</sup>, J. Kwon, J. Kim and H-S. Oh (2018). [Prediction of extremal precipitation by quantile regression forests: from SNU Multiscale team.](https://link.springer.com/article/10.1007/s10687-018-0323-y) *Extremes*, **21(3)**, 463--476.

5.  **S. Park** and H-S. Oh<sup>$*$</sup> (2017). [Spatio-temporal analysis of particulate matter extremes in Seoul: use of multiscale approach.](http://dx.doi.org/10.1007/s00477-016-1376-6) *Stochastic Environmental Research and Risk Assessment*, **31(9)**, 2401--2414.

```{=html}
<!--
1. **S. Park** and H-S. Oh<sup>$*$</sup> (2022). [Lifting scheme for streamflow data in river networks.](https://rss.onlinelibrary.wiley.com/doi/10.1111/rssc.12542) *Journal of the Royal Statistical Society: Series C (Applied Statistics)*, **71(2)**, 467--490. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. J. Kim, **S. Park**<sup>$*$</sup>, J. Kwon, Y. Lim and H-S. Oh (2021). [Estimation of spatio-temporal extreme distribution using a quantile factor model.](https://link.springer.com/article/10.1007/s10687-020-00404-0) *Extremes*, **24(1)**, 177--195. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. **S. Park**<sup>$*$</sup>, J. Kwon, J. Kim and H-S. Oh (2018). [Prediction of extremal precipitation by quantile regression forests: from SNU Multiscale team.](https://link.springer.com/article/10.1007/s10687-018-0323-y) *Extremes*, **21(3)**, 463--476. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`

1. **S. Park** and H-S. Oh<sup>$*$</sup> (2017). [Spatio-temporal analysis of particulate matter extremes in Seoul: use of multiscale approach.](http://dx.doi.org/10.1007/s00477-016-1376-6) *Stochastic Environmental Research and Risk Assessment*, **31(9)**, 2401--2414. `r text_spec("SCIE", background = "#990000", color = "#c894a8", bold = T)` `r text_spec("STAT-PROB", background = "#990000", color = "#c894a8", bold = T)`
-->
```
```{=html}
<!--
### Under Review
-->
```
```{=html}
<!--
1. S. Lee, **S. Park** and Y. Lim<sup>$*$</sup> (2021+). Prediction of extreme PM2.5 concentrations via extreme quantile regression. *Communications for Statistical Applications and Methods*, Accepted for publication.
-->
```
```{=html}
<!--
1. S. Cho, Y-M. Kim, G. Seong, S. Park, **S. Park**, S-E. Lee and Y. Park<sup>$*$</sup> (2022+). Analysis of on-ship transmission through cases of COVID-19 mass outbreak on Republic of Korea Navy Amphibious Warfare ship. *Epidemiology and Health]*.
-->
```
## Presentations

<!--
1. Spatial statistical models for environmental data in Korea, *JSS-KSS-CIPS Joint Meeting, Tokyo, Japan, September 2022.
-->

1.  Lifting scheme for streamflow data in river networks, *2022 The Korean Data Information Science Society Spring Conference*, Busan, Korea, May 2022.

2.  Lifting scheme for streamflow data in river networks, *2021 The Korean Statistical Society Autumn Conference*, Seoul, Korea, November 2021.

3.  Lifting scheme for streamflow data in river networks, *Bernoulli-IMS 10th World Congress in Probability and Statistics*, Seoul, Korea, July 2021.

4.  A new approach for modelling the spatial extent of agricultural drought, *The 55th Canadian Meteorological and Oceanographic Society (CMOS) Congress*, Victoria, Canada, June 2021.

5.  Multiresolution analysis for spatio-temporal data, *5th Institute of Mathematical Statistics Asia Pacific Rim Meeting*, Singapore, Singapore, June 2018.

6.  [Prediction of extremal precipitation: the use of quantile regression forests](http://www.eva2017.nl/program/scipro/friday/index.html), *10th Extreme Value Analysis Conference*, Delft, Netherlands, June 2017.

7.  Multiresolution analysis for spatio-temporal data. *2017 The Korean Statistical Society Spring Conference*, Seoul, Korea, May 2017.

8.  Multiscale modeling for particulate matter extremes. *2015 The Korean Statistical Society Autumn Conference*, Yongin, Korea, November 2015.

9.  [Multiscale modeling for particulate matter extremes in Seoul](http://data.si.re.kr/node/623). *The Seoul Institute Research Competition 2015*, Seoul, Korea, November 2015.

10. Prediction of extreme particulate matter : the use of quantile regression forests. *2014 The Korean Statistical Society Autumn Conference*, Seoul, Korea, November 2014.

## Awards

1.  Excellence award (3rd place), KSIAM-MathWorks problem challenge, *Korea Society for Industrial and Applied Mathematics*, Sep 2018.

2.  Best oral presentation award (Pre-PhD): Multiresolution analysis for spatio-temporal data. *The Korean Statistical Society*, May 2017.

3.  Excellence award, [The Seoul Institute Research Competition 2015](http://data.si.re.kr/node/623), *The Seoul Institute*, November 2015.

## Grants

### International or Domestic Research Foundations

-   Basic Science Research Program (기본연구), *Korean Ministry of Education*, June 2021 \~

### University Grants

-   신진교수 연구비 지원사업, *Chungbuk National University (CBNU)*, March 2021 \~ February 2022.

### Scholarship

-   Sohn Dong-Joon Scholarship, *College of Natural Sciences (SNU)*, May 2016 \~ August 2019.

## Refree

-   Journal of Agricultural, Biological and Environmental Statistics

-   Extremes

-   Stochastic Environmental Research and Risk Assessment

-   Computational Statistics

-   Journal of the Korean Statistical Society

-   Communications for Statistical Applications and Methods

-   Computational Statistics and Data Analysis

## Teaching

### Chungbuk National University

#### Undergraduate Level Courses

-   Elementary Probability Theory (2022 Spring)

-   Regression Analysis (2021 Spring, 2022 Spring)

-   Statistical Simulation (2021 Spring)

-   Insurance Statistics (2021 Fall)

-   Financial Statistics (2021 Fall)

-   Financial and Insurance Statistics (2022 Fall)

-   Spatial Statistics (2022 Fall)

#### Graduate Level Courses

-   Topics in Regression Analysis (2022 Spring)

-   Statistical Methodology (2021 Spring)

-   Machine Learning Methodology (2022 Fall)

-   Deep Learning (2021 Fall)
:::

## Contact Me

[pscstat\@gmail.com](mailto:pscstat@gmail.com)
